Project Review Template

### 2023-05-01 Reviews/YaoLuReviews.qmd

---
title: Project Review Template 
author: Annabella Hines
date: "`r file.mtime(knitr::current_input())`"
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Title of project: A Match Made in Landfills? Exploring the diversity and burden of antimicrobial resistance genes carried by white stork (Ciconia ciconia) throughout the breeding season in Madrid, Spain

Name of project author(s): Raquel Francisco and Seth Lattner

Name of project reviewer: Annabella Hines

# Specific project content evaluation
Evaluate the different parts of the project by filling in the sections below.

@@

I really enjoyed your abstract and background sections; they gave great context to the questions you were trying to answer and helped me understand how it fits into the existing research and work in that field. I like the abundance of information and the references and summaries of previous work

@@

You had very clear and succinct hypotheses that made sense in the context of the data and the objectives you outlined earlier.

@@

There is a codebook provided to explain the variables in the data. The data and its source was described well. If it is feasible, I would've liked a summary table of the data in the manuscript just to reference back to.

@@

I thought the exploration of the data was very thorough and the cleaning as well. The decision to not use 2020 data in the analysis was well explained and supported. Some alternatives were discussed and the most meaningful exploratory results were presented in the manuscript.

@@

The basic statistical analysis section was included in the manuscript but it still had the template instructions left in. I see you did do some in the StatisticalAnalysis_ModelFitting.qmd so just choosing the most relevant and moving it over to the manuscript is all you have left. The full analysis statistical models were included and well explained, so I think adding the simple ones may just help the flow to show the steps to how you got to what you did next.

@@

* strong and reasonable analysis

@@

The summary and interpretation section could be expanded upon and explained a bit better. The information in parentheses may be better understood by explaining it in a following sentence. I thought the figures were pretty good, I'd just make them more aesthetically pleasing and make the size a bit larger so they are more clearly legible in the manuscript. It seems some figures weren't made or inserted yet as there were captions but just empty space about them.

@@

The conclusions covered the main results well, however I think they could still be fleshed out a bit more. The limitations seemed to have the general idea but also needs detail. The findings were interpreted appropriately based on the figures and results presented.

@@

Overall I'm really enjoying the lay out and detail of your project. I just think the conclusions and results may need to be more thought out to match the in depth nature of the introduction and background.

# Overall project content evaluation

@@

All the files make sense and the junk files were removed or had an explanation as to why they were empty. I like the numbering system in the main directory as it makes it the order to view and run the files very clear.

@@

The code and project overall are well documented with adequate supporting files and explanatory information. Each step made sense and had a logical flow from one to the other.

@@

I had trouble reproducing some things in you statistical analysis files but I'm pretty that was just a problem on my end or not. When I tried to load certain packages like ggplot2 or see I got errors about the version. Other than that, everything was fully reproducible without edits.

@@

Alternatives were discussed for data processing and models with thorough assessment of their validity and performance. The hypotheses were fully addressed by the statistical tests that were ran.

@@

* strong level of thoroughness

@@

Overall you both have done a great job, keep up the good work and little fixes to put the final touches on it!

>>>>

@@

Title of project:Exploring the diversity and burden of antimicrobial resistance genes carried by white stork (Ciconia ciconia) throughout the breeding season in Madrid, Spain

Name of project author(s):Raquel Francisco and Seth Latter

Name of project reviewer:Yao Lu

@@

Good context description. Introduction is detailed.

@@

Question(s)/hypotheses are placed in a obvious place.

@@

Codebook is provided.

@@

Good exploratory.  Missing check , correlation plot and pairwise check are good.

@@

If there is no specific reason why we should limit the number of variables into 2 or 3.You can try multivariable GLM and finally select a set of variables to fit the model. That way should produce a very competitive model to your current glmer_fit_11. RMSE should be(99% possibility) less than your current model if not equal to. AICs and BICs are not sure but it has high possibility of better.

As your check_model(glmer_fit_11) shows, the Normality of Residuals(QQ plot) shows abnormal. It looks like this model is polarization. Which means in this model. glmer_fit_11 will predict the outcome either overestimate much or underestimate much, even it's the best GLM model compare to the other models you choose. This is not we want. Since you did much great job in other part. If you don't have time to go further at this part. Mentioning this abnormal to the readers should be helpful when others want to process you product. To address this abnormal, the easiest way is to do transformation to dependent variable or predictors. Such as boxcox transformation or basic log transformation.

As your MLp shows, I am not sure how Multi-Drug Resistence measure. But in that plot, it looks like a dichotomic variable. For dichotomic variables, we usually use mixed effect logistic regression other than linear. And this is the reason why the QQ plot show like that. When we use linear regression to model dichotomic variable, the QQ plot will looks like the one in 'check_model(glmer_fit_11)'.

@@

* defensible but not optimal analysis

@@

Miss table title in page13. Also I think you can simplify this table by deleting some columns, such as AICc_wt, since it reflect the same thing as Performance_Score. Also you can round it to 2 or 3 digits to make it narrow. And show other performance, as you did a great job like in your 'Comparison of Model Indices' plot. Why not move those evaluation value to here.

The two table are close which make me think if they are one table at the beginning.

in the second table. page13

Negative sign is separated with the number 4.302130.

@@

'makes sense because in your prior papers you have found increase nest success with increased LUI' page 14.

Not all audience have that paper.

@@

@@

Well structured and easy to follow.

@@

good information and easy to understand.

@@

All code can be run without issues.

@@

Some figures are all white in docx in my computer. But I find those in the result folder. There are many good plots in the StatiscalAnalysis_ModelFitting_R. I think some of those can be processed a little bit and showed in the manuscripts. Like 'Comparison of Model Indices' and those statistical plots.

@@

* strong level of thorougness

@@

Good background discussion. Good exploratory analysis, such as coefficients check, pairwise check. 
Mixed effect logistic regression maybe more competitive than your current model systematically as one of your outcome looks like dichotomous(I am not sure if that variable should be). Variable selection by p-value in multivariable mixed effect model may also produce a more competitive model, if there is no specific reason why limit the number of predictors in 2 or 3.
